Algebraic File Synchronization: Adequacy and Completeness

### 2017-10-15 p2/rec-sound.tex
Fixed the soundness proof. Inverses are needed after all.

\noindent
We would like to prove that $\worksmbx{A,B}{B\cc \reca}$.
From \cref{can_move_intersection} above we know that we can move commands in $\acbnp$
to the beginning of $A$ and $B$, and so this is equivalent to
\[ \worksmbx{\acb\cc\amb, \acb\cc\bma}{\acb\cc \bma\cc \reca}, \]
which is equivalent to
\[ \worksmbx{\amb, \bma}{\bma\cc \reca}. \]

For ease of reading, let us rename
$\amb$ to $S$,
$\reca$ to $S^*$,
and $\bma$ to $T$.
In this notation, we intend to prove that
\[ \worksmbx{S,T}{T\cc S^*}. \]
We can do so if we can show that
\[ \worksmbx{S,T}{S^*}. \]

This is because 
$\worksmbx{S,T}{T}$ is trivially true, and this, combined with the above,
yields 
$ \worksmbb{S,T}{S^*,T}. $
As $\reca\indep\bma$, that is, $S^*\indep T$,
from \cref{combine_independent_sequences}
we know
$ \worksmbx{S^*,T}{T\cc S^*}, $
and as $\worksmeqsign$ is transitive, combining the two statements above
gives $\worksmbx{S,T}{T\cc S^*}$.

@@

TODO TODO TODO TODO TODO

\noindent
To restate some results above, we therefore already know the following:
\begin{itemize}
\item $\amb$ and $\bma$ are simple as $A$ and $B$ are simple
\item $\amb \cap \bma = \emptyset$
\item $\reca$ is the largest subset of $\amb$ for which $\reca\indep\amb$
% TODO Inverse is used here - how/why?
\item $\worksmbb{\acbi\cc A,\acbi\cc B}{\amb, \bma}$ 
because of \cref{r_invmove}
as $\worksmbb{A,B}{A,B}$,
and $A\equiv\acb\cc\amb$, and $B\equiv\acb\cc\bma$.
TODO HOW IS THIS USED?
\end{itemize}

Our theorem is therefore proven if we prove the following lemma,
in which we rename $\amb$ to $S$, $\reca$ to $S^*$, and $\bma$ to $T$:
\newcommand{\condSimple}{(c1)}
\newcommand{\condDisj}{(c2)}
\newcommand{\condApr}{(c3)}
\newcommand{\condWork}{(c4)}
\begin{mylem}\label{reconciliation_correct_part}
If
   \begin{itemize}
   \item[\condSimple] $S$ and $T$ are simple sequences,
   \item[\condDisj] $S\cap T=\emptyset$,
   \item[\condApr] $S^*$ is the largest subset of $S$ where $S^*\indep T$, and
   \item[\condWork] $\worksmxb{\sqs{C}}{S,T}$ for some set of sequences $\sqs{C}$,
   \end{itemize}
then
\[ \worksm{\sqs{C}}{S^*}. \]
\end{mylem}

\begin{proof}
This is trivial unless $\worksmnil{\sqs{C}}$, so we will assume that it is true
and therefore $\worksmnilb{S,T}$.

The proof is similar to that of \cref{can_move_intersection}.
We mark all commands in $S$ that are in its subset $S^*$, and
we prove that $S$ can be transformed into $S'$
so that all marked commands would be at its beginning.
If so, then 
$\worksm{\sqs{C}}{S^*}$ 
based on \cref{worksextpostfix}
as $\worksm{\sqs{C}}{S'}$ and $S'=S^*\cc S_0$ 
where $S_0$ contains the remaining (conflicting) commands.

@@

In the last two cases, we know that either $m=\parent(n)$ or $n=\parent(m)$.
We also know that because of {\condApr} there must be 
a command $\cqrov$ in $T$ which is not independent of $\czwmv$
as $\czwmv$ is not part of $S^*$.
\begin{gather*}
S = \cdots\cc  \czwmv\cc  \cxynv\cc  \cdots \\
T = \cdots\cc  \cqrov\cc \cdots
\end{gather*}
We know none of these commands is an assertion command, and 
from {\condDisj} that $\cqrov\neq\czwmv$.
Therefore, based on \cref{incomparable_is_independent} we know this means that
either $m\descendantEq o$ or $o\descendantEq m$.
From {\condApr} we also know that $\cxynv\indep \cqrov$,
and so because of \cref{incomparable_is_independent},
$n\unrel o$.

We therefore have four cases considering the relationships between $n,m$ and $o$:
\begin{itemize}
\item $n=\parent(m) \wedge o\descendantEq m$.
   This would mean that $o\descendantEq n$ or $n=\parent(o)$, which contradicts $n\unrel o$.
\item $n=\parent(m) \wedge m\descendantEq o$.
   This would mean that $n\descendant o$, which contradicts $n\unrel o$.
\item $m=\parent(n) \wedge o\descendantEq m$.
   This would mean that $o\descendant n$, which contradicts $n\unrel o$.
\item $m=\parent(n) \wedge m\descendantEq o$.
   Let us continue with this case.
\end{itemize}

We know that $T$ cannot have a command on $m$ as $m=\parent(n)$ and $\cxynv\indep T$,
and so $m\neq o$ and therefore $m\descendant o$.
This means we can create a new sequence $T'\equiv T$ by inserting a command on 
$m$ into $T$ before $\cqrov$
according to \cref{ax_parent_assert}.
We now have $\cxynv\indep T\equiv T'$, which is a contradiction as
$T'$ has a command on $m$ and $m=\parent(n)$.
\end{proof}

>>>>

\noindent
We would like to prove that $\worksmbx{A,B}{B\cc \reca}$.
From \cref{can_move_intersection} above we know that we can move commands in $\acbnp$
to the beginning of $A$ and $B$, and so this is equivalent to
\[ \worksmbx{\acb\cc\amb, \acb\cc\bma}{\acb\cc \bma\cc \reca}. \]

For ease of reading, let us rename
\begin{itemize}
\item $\amb$ to $S$
\item $\reca$ to $S^*$
\item $\bma$ to $T$
\item and $\acb$ to $U$.
\end{itemize}
In this notation, we intend to prove that
\[ \worksmbx{U\cc S,U\cc T}{U\cc T\cc S^*}. \]
We can do so if we can show that
\[ \worksmbx{S,T}{S^*}. \]

This is because from \cref{indep_prefix_combine} we know
$\worksmbx{U\cc T, U\cc S^*}{U\cc T\cc S^*}$ as $S^* \indep T$.
From $\worksmbx{S,T}{S^*}$ trivially
$\worksmbb{S,T}{S^*, T}$,
and from \cref{works_restricted} we know
$\worksmbb{U\cc S, U\cc T}{U\cc S^*, U\cc T}$.
Because $\worksmeqsign$ is transitive, combining these results
we get $\worksmbx{U\cc S,U\cc T}{U\cc T\cc S^*}$.

@@

\noindent
To restate some results above, we therefore already know the following:
\begin{itemize}
\item $S=\amb$ and $T=\bma$ are simple as $A$ and $B$ are simple
\item $S\cap T = \amb \cap \bma = \emptyset$
\item 
$S^*$ is the largest subset of $S$ for which $S^*\indep T$, as
$\reca$ is the largest subset of $\amb$ for which $\reca\indep\bma$
\end{itemize}

Our theorem is therefore proven if we prove the following lemma.
\newcommand{\condSimple}{(c1)}
\newcommand{\condDisj}{(c2)}
\newcommand{\condApr}{(c3)}
\begin{mylem}\label{reconciliation_correct_part}
If
{\condSimple} $S$ and $T$ are simple sequences,
{\condDisj} $S\cap T=\emptyset$,
and {\condApr} $S^*$ is the largest subset of $S$ where $S^*\indep T$,
then
$\worksmbx{S,T}{S^*}$.
\end{mylem}

\begin{proof}
This is trivial unless $\worksmnilb{S,T}$, so we assume that it is the case.

The proof is similar to that of \cref{can_move_intersection}.
We mark all commands in $S$ that are in its subset $S^*$, and
we prove that $S$ can be transformed into $S'$
where all marked commands are at the beginning.
If so, then 
$\worksm{S}{S^*}$ based on \cref{worksextpostfix},
from which trivially $\worksmbx{S,T}{S^*}$.

@@

In the last two cases, we know that either $m=\parent(n)$ or $n=\parent(m)$.
We also know that because of {\condApr} there must be 
a command $\cqrov$ in $T$ which is not independent of $\czwmv$
as $\czwmv$ is not part of $S^*$.
\begin{gather*}
S = \cdots\cc  \czwmv\cc  \cxynv\cc  \cdots \\
T = \cdots\cc  \cqrov\cc \cdots
\end{gather*}
Based on \cref{incomparable_is_independent} we know this means that
either $m\descendantEq o$ or $o\descendantEq m$.
From {\condApr} we also know that $\cxynv\indep \cqrov$,
and so because of \cref{incomparable_is_independent},
$n\unrel o$.
We also know none of these commands is an assertion command, and 
from {\condDisj} that $\cqrov\neq\czwmv$.

We therefore have four cases considering the relationships between $n,m$ and $o$:
\begin{itemize}
\item $n=\parent(m)$ and $o\descendantEq m$.
   This would mean that $o\descendantEq n$ or $n=\parent(o)$ (if $o=m$), which contradicts $n\unrel o$.
\item $n=\parent(m)$ and $m\descendantEq o$.
   This would mean that $n\descendant o$, which contradicts $n\unrel o$.
\item $m=\parent(n)$ and $o\descendantEq m$.
   This would mean that $o\descendant n$, which contradicts $n\unrel o$.
\item $m=\parent(n)$ and $m\descendantEq o$.
   Let us continue with this case.
\end{itemize}

As $m=\parent(n)$, we know $\czwmv\cc\cxynv$ must be a construction pair.
We know that $T$ cannot have a command on $m$ as $m=\parent(n)$ and $\cxynv\indep T$,
and so $m\neq o$ and therefore $m\descendant o$.
This means we can create a new sequence $T'\equiv T$ by inserting a command on 
$m$ into $T$ before $\cqrov$
according to \cref{ax_parent_assert}, the input type of which is $[\vald]$.
As $T'$ is still minimal, and $\worksmnilb{S,T}$,
from \cref{worksinputmatch} we get $[z]=[\vald]$, which is a contradiction,
as $\czwmv$ is the first command in a construction pair.
\end{proof}
